|

### 2018-12-13 paper.Rmd
Added orca exported graph.

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan, however, right now there is no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. See Figure \@ref(fig:fig-3) below.      
There seems to be a new engine for exporting graphs locally without relying on the plotly server --- which you wanna avoid for a properly reproducible PDF --- called orca (`?orca`). However, the [installation](https://github.com/plotly/orca#installation) is too challenging for the average user at the moment.

```{r fig-3, fig.align="center", fig.cap="Scatterplot of Speed and Distance", fig.pos="H", message=FALSE, warning=FALSE}
library(plotly)
plot_ly(cars, type = "scatter", mode="markers",
        x=~speed, 
        y=~dist)
```

>>>>

## Plotly graphs
Plotly is a popular graph engine that let's you also produce interactive graphs that you can embed in html webpages or documents (e.g., see [here](https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/)). I am a big fan. For some time there was no easy, automatic way to insert high resolution Plotly graphs into your R Markdown PDF. However, this changed since Plotly provided Orca, a command line application for generating static images from Plotly graphs. The installation is a bit tricky (see here: https://github.com/plotly/orca#installation) but once you get it running you can produce beautiful graphs and include them in your RMarkdown PDF using some simple latex as shown below in Figure \@ref(fig:fig-3).

```{r fig-3, message=FALSE, warning=FALSE}
library(plotly)
p <- plot_ly(cars, type = "scatter", mode="markers",
        x=~speed, 
        y=~dist)
Sys.setenv('MAPBOX_TOKEN' = '12423423') # set arbitrary token
orca(p, "plotly-plot.pdf")
```

\begin{figure}[H]
\centering
\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
		\includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
\begin{flushleft}
\end{flushleft}
\end{figure}
\vspace{-1.2cm}

### 2018-12-13 paper.tex
Added orca exported graph.

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{5 November, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan, however, right now there is no easy, automatic way to
insert high resolution Plotly graphs into your R Markdown PDF. See
Figure \ref{fig:fig-3} below.\\
There seems to be a new engine for exporting graphs locally without
relying on the plotly server --- which you wanna avoid for a properly
reproducible PDF --- called orca (\texttt{?orca}). However, the
\href{https://github.com/plotly/orca\#installation}{installation} is too
challenging for the average user at the moment.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(plotly)}
\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics{paper_files/figure-latex/fig-3-1}

\caption{Scatterplot of Speed and Distance}\label{fig:fig-3}
\end{figure}

@@

\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}

@@

>>>>

  \title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address:
  \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}.
  Acknowledgments: I am grateful to all those generous people that
  invest their time into open-source software.}\vspace{0.5cm}\\}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{13 December, 2018\\[2\baselineskip]Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

Plotly is a popular graph engine that let's you also produce interactive
graphs that you can embed in html webpages or documents (e.g., see
\href{https://paulcbauer.shinyapps.io/visualizing-causal-scenarios/}{here}).
I am a big fan. For some time there was no easy, automatic way to insert
high resolution Plotly graphs into your R Markdown PDF. However, this
changed since Plotly provided Orca, a command line application for
generating static images from Plotly graphs. The installation is a bit
tricky (see here: \url{https://github.com/plotly/orca\#installation})
but once you get it running you can produce beautiful graphs and include
them in your RMarkdown PDF using some simple latex as shown below in
Figure \ref{fig:fig-3}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(plotly)}
\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}
        \DataTypeTok{x=}\OperatorTok{~}\NormalTok{speed, }
        \DataTypeTok{y=}\OperatorTok{~}\NormalTok{dist)}
\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]
\centering
\caption{An plotly plot that was exported as PDF with orca before}\label{fig:fig-3}
        \includegraphics[width=0.9\linewidth]{plotly-plot.pdf}
\begin{flushleft}
\end{flushleft}
\end{figure}

\vspace{-1.2cm}

@@

\NormalTok{p <-}\StringTok{ }\KeywordTok{plot_ly}\NormalTok{(cars, }\DataTypeTok{type =} \StringTok{"scatter"}\NormalTok{, }\DataTypeTok{mode=}\StringTok{"markers"}\NormalTok{,}

@@

\KeywordTok{Sys.setenv}\NormalTok{(}\StringTok{'MAPBOX_TOKEN'}\NormalTok{ =}\StringTok{ '12423423'}\NormalTok{) }\CommentTok{# set arbitrary token}
\KeywordTok{orca}\NormalTok{(p, }\StringTok{"plotly-plot.pdf"}\NormalTok{)}
